Graphical Tests for Power Comparison of Competing Designs

### 2012-03-28 setup.tex
working on intro, added/fixed references
added images

XXX picture of sampling size?
An additional factor we were interested in this particular situation was to assess, how much of the data we actually needed to use in a design to have observers pick out the pattern. Clearly, a design is more efficient, if a smaller sample size is sufficient for showing the presence of a relationship. In order to investigate this, we took different size samples of the data and created lineup plots of all four designs for these subsets. Another perturbation to the data are `shifts' in wind direction, i.e. we make use of the circular nature of the wind direction and adjust the $x$ axis by using different offsets.
XXXX show picture of offsets
 This results in a shift of the wave in Euclidean charts and a rotation in the polar charts. Our initial hypothesis was that this would have no effect on the polar charts, but might have a deteriorating effect on the Euclidean charts, in the case that the peak or the valley of the wave was at either end of the $x$ axis. 
While these simple perturbations and different sample sizes allow us to get insight into different aspects of the designs, they also allow us to get multiple responses from each observer to assess individual ability without the need to go outside the framework of the original data, i.e. we leave the joint relationship between $x$ and $y$ essentially unchanged. For all of these combinations we produced two replicates, resulting in a total of 192 different lineups ($ 4 \text{ designs} \times 6 \text{ sample sizes} \times 4 \text{ offsets} \times 2 \text{ reps})$.

@@

Most generally this experiment can be paralleled to the pie chart versus barchart discussion \cite{}. 
The Euclidean coordinate plot is made up of bars where areas are colored proportionally according to percentages. The polar coordinate plot is made up of pie slices which are also colored proportionally according to the data. 
Viewers of these charts will visually decode the areas of the bars and pie slices and make a judgement based on their decoding. According to  \citet[page=40]{kosslyn:2006}, area is usually perceived as a function of what the actual area is. This function is the area raised to an exponent of approximately 0.8 and then multiplied by a constant. However, when bars are parallel, the relative height of these bars is perceived very accurately. From this information, one could infer that the Euclidean coordinate plot may gain efficiency based on the height of the colored bars.

>>>>

XXX picture of sampling size?
An additional factor we were interested in this particular situation was to assess, how much of the data we actually needed to use in a design to have observers pick out the pattern. Clearly, a design is more efficient, if a smaller sample size is sufficient for showing the presence of a relationship. In order to investigate this, we took different size samples of the data and created lineup plots of all four designs for these subsets. Another perturbation to the data are `shifts' in wind direction, i.e. we make use of the circular nature of the wind direction and adjust the $x$ axis by using different offsets.
XXXX show picture of offsets
\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=\linewidth]{euclid-offset} 
   \caption{ \label{fig:offset}Euclidean charts of the same sample, with shifts in wind direction by 90, 180, and 270 degrees. The shift by 90 and 270 leads to a `valley' versus a `mountain' pattern, whereas a shift by 180 degrees inverts the wave pattern from `down-up' to `up-down'.}
\end{figure}

 This results in a shift of the wave in Euclidean charts and a rotation in the polar charts. Our initial hypothesis was that this would have no effect on the polar charts, but might have a deteriorating effect on the Euclidean charts, in the case that the peak or the valley of the wave was at either end of the $x$ axis. 
While these simple perturbations and different sample sizes allow us to get insight into different aspects of the designs, they also allow us to get multiple responses from each observer to assess individual ability without the need to go outside the framework of the original data, i.e. we leave the joint relationship between $x$ and $y$ essentially unchanged. For all of these combinations we produced two replicates, resulting in a total of 192 different lineups ($ 4 \text{ designs} \times 6 \text{ sample sizes} \times 4 \text{ offsets} \times 2 \text{ reps})$.

@@

Most generally this experiment can be paralleled to the pie chart versus barchart discussion \cite{***}. 
The Euclidean coordinate plot is made up of bars where areas are colored proportionally according to percentages. The polar coordinate plot is made up of pie slices which are also colored proportionally according to the data. 
Viewers of these charts will visually decode the areas of the bars and pie slices and make a judgement based on their decoding. According to  \citet[page=40]{kosslyn:2006}, area is usually perceived as a function of what the actual area is. This function is the area raised to an exponent of approximately 0.8 and then multiplied by a constant. However, when bars are parallel, the relative height of these bars is perceived very accurately. From this information, one could infer that the Euclidean coordinate plot may gain efficiency based on the height of the colored bars.
